Artificial ecosystem selection to deduce the mapping between microbial community structure and ecosystem function

### 2021-07-27 Manuscript/manuscript.Rmd
update manuscript text

>>>>

Why haven't we been more successful in identifying relationships between
microbial community structure and ecosystem functions? Microbial communities
are super diverse, particularly in soil environments, and
looking at the whole community using broad phylogenetic markers such as 16S
makes it difficult to sift through all of that diversity to find informative
markers. Looking at individual protein-coding genes manages to reduce that
diversity, but it also assumes we know what limits the rate of a process in a
particular ecosystem. Typically, we choose the gene that encodes the final step
in a pathway - for example, the mcrA gene, which encodes a subunit of the
enzyme the performs the final step in the methanogenesis pathway. However,
regulation may happen further up stream within the pathway and therefore the
abundance of the final gene wouldn't correlate with the rate of the process.
In fact, the limitation may be in substrate creation by other functional groups
unrelated to methanogens. To overcome these challenges, we chose a
